SMT-Boosted Security Types for Low-Level MPC

### 2024-10-14 esop25/examples.tex
checkpoint

We consider examples that illustrate the versatility of the $\TirName{Encode}$
typing rule for confidentiality, the use of postconditions for correctness,
and the use of both pre-~and postconditions for integrity.

@@

The $\ttt{encode}$ function example in Section \ref{section-metalangty}
illustrates the use of type annotations to track confidentiality. In
2-party Yao's Garbled Circuits (YGC), a \emph{garbler} prepares a circuit encoding
that is shared with a \emph{evaluator}, and the $\ttt{encode}$ function
defines the method the garbler uses to share their input secret encodings
with the evaluator. The example illustrates how confidentiality is reflected
in its (cipher)type.

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar
to BDOZ as described in Section \ref{section-ipj}. In our definition
of GMW we use the convention that shared values $\macgv{w}$ are identified by
strings $w$ and encoded as shares $\mx{w}{1}$ and $\mx{w}{2}$.  As for
YGC, ciphertypes reflect the confidentiality of GMW input encodings as
defined in the $\ttt{encodegmw}$ function in Figure \ref{fig-gmw}. No
programmer annotation is needed given the syntax of the function
body. More interestingly, the $\ttt{andgmw}$ gate definition shows how
a programmer hint can express the relevant confidentiality property of
the output share $\mx{z}{2}$ on client 2. The non-trivial equivalence
can be verified by SMT once during verification, and subsequently
confidentiality is expressed in the dependent type of the function
(as for $\ttt{encode}$).

@@

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{w}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{w}$.

@@

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which would subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given this, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $\fcod{a * b} = c$, unique per multiplication
gate, that are secret shared with clients during pre-processing.
In our encoding we assume the additional convention that each gate
output identifier distinguishes the Beaver triple, so for
example the share of the $a$ value for a gate $\ttt{"g1"}$
is identified by $\ttt{"g1as"}$, etc., and $\eqspre$ would
subsume the following constraints for the $a,b,c$ values of
gate $\ttt{"g1"}$.
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}
The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.

>>>>

In Section \ref{section-smt} we gave the example of 3-party additive
sharing for any field $\fieldp{p}$. In Sections \ref{section-ipj} and
\ref{section-metalangty} we discussed the example of YGC input encoding.
Now we consider examples that illustrate the versatility of the
$\TirName{Encode}$ typing rule for confidentiality, the use of
postconditions for correctness, and the use of both pre-~and
postconditions for integrity.

Using the Satisfiability Modulo Fields theory in cvc5 on an Apple M1
processor, we have verified correctness of additive sharing protocols
in fields up to size $\fieldp{2^{31} - 1}$ (an approximation of 32-bit
integers) which takes ~16ms to compute for 3 parties and not
significantly more than for, e.g., $\fieldp{2}$. We have also verified
the semi-homorphic encryption properties leveraged in the BDOZ circuit
library functions (Figures \ref{fig-bdozsum} and \ref{fig-bdozmult}) in
fields up to size $\fieldp{2^{31} - 1}$ which takes \cnote{TBD}ms for the
property used for the postcondition of the $\ttt{mult}$ gate. This is
categorically better performance than could be achieved using previous
brute-force methods in $\fieldp{2}$ \cite{skalka-near-ppdp24}.

@@

In the 2-party GMW protocol \cite{evans2018pragmatic}, another garbled
binary circuit protocol, values are encrypted in a manner similar to
BDOZ as described in Section \ref{section-ipj}. In our definition of
GMW we use the convention that shared values $\macgv{\mesg{w}}$ are
identified by strings $w$ and encoded as shares $\mx{w}{1}$ and
$\mx{w}{2}$.  As for YGC, ciphertypes reflect the confidentiality of
GMW input encodings as defined in the $\ttt{encodegmw}$ function in
Figure \ref{fig-gmw}. No programmer annotation is needed given the
syntax of the function body. More interestingly, the $\ttt{andgmw}$
gate definition shows how a programmer hint can express the relevant
confidentiality property of the output share $\mx{z}{2}$ on client
2. The non-trivial equivalence can be verified by SMT once during
verification, and subsequently confidentiality is expressed in the
dependent type of the function (as for $\ttt{encode}$).

@@

Returning to the example of malicious-secure 2-party BDOZ arithmetic
circuits begun in Section \ref{section-ipj}, in Figure \ref{fig-bdozsum} we
define $\ttt{sum}$ and $\ttt{open}$ functions. The latter implements
``secure opening''-- each party sends it's local share of a
global value $\macgv{\mesg{w}}$ along with its MAC to the other party,
which is authenticated via the $\macbdoz{w}$ check (in \ttt{\_open}),
and then each party reconstructs $\macgv{\mesg{w}}$.

@@

In BDOZ a pre-processing phase is assumed where initial input secrets
are shared along with their associated MACs and keys. This can be
expressed in $\eqspre$ for input secrets $\sx{\ttt{"x"}}{1}$ and
$\sx{\ttt{"y"}}{2}$, for example, which subsume the following
constraints on shares:
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"xs"}}{2} \eop \sx{\ttt{"x"}}{1} \fminus \rx{\ttt{"x"}}{1} \wedge 
\mx{\ttt{"xs"}}{1} \eop \rx{\ttt{"x"}}{1} \wedge \\
\mx{\ttt{"ys"}}{1} \eop \sx{\ttt{"y"}}{2} \fminus \rx{\ttt{"y"}}{2} \wedge 
\mx{\ttt{"ys"}}{2} \eop \rx{\ttt{"y"}}{2} 
\end{array}
$$}
and the following constraint on keys and MACs for authentication
of $\sx{\ttt{"x"}}{1}$ (and similarly for $\sx{\ttt{"y"}}{2}$):
{\footnotesize$$
\begin{array}{l}
\mx{\ttt{"delta"}}{1} \eop \rx{\ttt{"delta"}}{1} \wedge
\mx{\ttt{"xk"}}{1} \eop \rx{\ttt{"xk"}}{1} \wedge\\
\mx{\ttt{"xm"}}{2} \eop \mx{\ttt{"xk"}}{1} \fplus (\mx{\ttt{"delta"}}{1} * \mx{\ttt{"xs"}}{2})
\end{array}
$$}
Given this, a malicious secure opening of $\sx{\ttt{"x"}}{1} +
\sx{\ttt{"y"}}{2}$ would be obtained as
$\ttt{sum}(\ttt{"z"},\ttt{"x"},\ttt{"y"}); \ttt{open}(\ttt{"z"})$.

A common approach to implementing multiplication gates in a BDOZ
setting is to use \emph{Beaver Triples}. Recall that Beaver triples
are values $a,b,c$ with $a$ and $b$ chosen randomly and $c = a * b$,
unique per multiplication gate, that are secret shared with clients
during pre-processing.  In our encoding we assume the additional
convention that each gate output identifier distinguishes the Beaver
triple, so for example the share of the $a$ value for a gate
$\ttt{"g1"}$ is identified by $\ttt{"g1as"}$, etc., and $\eqspre$
subsumes the following constraints for the $a,b,c$ values of gate
$\ttt{"g1"}$.  {\footnotesize$$
\begin{array}{l}
\mx{\ttt{"g1as"}}{1} \eop \rx{\ttt{"g1as"}}{1}\ \wedge 
\mx{\ttt{"g1bs"}}{1} \eop \rx{\ttt{"g1bs"}}{1}\ \wedge\\
\mx{\ttt{"g1as"}}{2} \eop \rx{\ttt{"g1as"}}{2}\ \wedge 
\mx{\ttt{"g1bs"}}{2} \eop \rx{\ttt{"g1bs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{1} \eop \\
\qquad ((\mx{\ttt{"g1as"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})\ \ftimes\\
\qquad\phantom{(}(\mx{\ttt{"g1bs"}}{1} \fplus \mx{\ttt{"g1bs"}}{2})) \fminus \rx{\ttt{"g1cs"}}{2}\ \wedge\\
\mx{\ttt{"g1cs"}}{2} \eop \rx{\ttt{"g1cs"}}{2}
\end{array}
$$}
The definition of the $\ttt{mult}$ gate is presented in Figure
\ref{fig-bdozmult}, where we present just client 1's side of the
protocol $\ttt{\_mult1}$ (client 2's side is nearly symmetric but with
a small variation-- refer to
\cite{evans2018pragmatic,10.1007/978-3-030-68869-1_3} for more
details).  We could call this function on input secrets
$\sx{\ttt{"x"}}{1}$ and $\sx{\ttt{"y"}}{2}$ in gate $\ttt{"g1"}$ as
$\ttt{mult}(\ttt{"g1"},\ttt{"x"},\ttt{"y"})$, for example, or embed
this gate internally in a circuit.
